Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-31 paper.qmd
Repositioned tsne_5 img

## Add arrows
arrow_df_pbmc <- tibble(x = c(94, 245, 105, 150),
             xend = c(96, 263, 94, 180),
             y = c(10.06, 9.72, 9.88, 9.855),
             yend = c(10.14, 10, 9.79, 10))

>>>>

## Add arrows
arrow_df_pbmc <- tibble(x = c(94, 273, 101, 150),
             xend = c(96, 295, 94, 180),
             y = c(10.06, 9.7, 9.88, 9.855),
             yend = c(10.14, 9.8, 9.85, 10))
